---
title: "Project Phoenix learnR UNAM"
subtitle: "R Markdown & Github"
author: "Dr Paul Brennan - Cardiff University"
date: "14 June 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## We used Rmarkdown

- All our handouts were prepared with Rmd
- They are available on Github <https://github.com/MarkKelson/learnR/>


## Here is a graph from yesterday

```{r, echo = FALSE}
library(ggplot2)
fileName <- "Namibia_region_urbanRural.csv"
path <- "/Users/paulbrennan/Documents/learnR/data/"
data <- read.csv(file = paste0(path,fileName))
ggplot(data = data[data$region=="Namibia",],
       aes( x = as.factor(Date), 
            y = Value,
            fill = residence)) +
  geom_bar(stat = "identity")
```

## Here is the code

```{r, echo=TRUE, eval=FALSE}
ggplot(data = data[data$region=="Namibia",],
       aes( x = as.factor(Date), 
            y = Value,
            fill = residence)) +
  geom_bar(stat = "identity")
```

## Lot's of online resources
- Check out the Rmarkdown Cheatsheet
- Look at the R-Studio website
